Analyses

### 2023-05-12 analyses.Rmd
- major updates before submission - language, analyses, commenting

@@

# define packages
packages <- 
  c(
    "brms", 
    "cowplot", 
    "devtools", 
    "english", 
    "faoutlier", 
    "GGally", 
    "gganimate",
    "kableExtra", 
    "knitr", 
    "lavaan", 
    "magrittr",
    "marginaleffects",
    "MVN", 
    # "psych", 
    "pwr", 
    "quanteda", 
    "semTools", 
    "tidyverse", 
    "td"
    )

@@

@@

@@

    # take logarithm
    words_log = log1p(words)
  )

@@

We filtered participants who answered the questionnaire in less than three minutes, which we considered to be unreasonably fast.

@@

We inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.

@@

# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]

@@

# Measures
## Privacy concerns
### Items

@@

@@

@@

@@

&nbsp;&nbsp;&nbsp;1. The other users seemed trustworthy.  
&nbsp;&nbsp;&nbsp;2. The operators of the participation platform seemed trustworthy.  
&nbsp;&nbsp;&nbsp;3. The website seemed trustworthy.

@@

@@

Note that we constrained Items 5 and Item 9 to be equal. Explanation: First, they are theoretically related. Second, not constraining would yield to just-identified model, for which model fit cannot be interpreted meaningfully.

@@

```{r}
name <- "trust_spec"
model <- "
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09

  trust =~ trust_community + trust_provider + trust_system
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

@@

Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.

```{r}
name <- "trustspec"
model <- "
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

```{r}
inspect(
  fit,
  what = "std"
  ) %$%
  lambda
```
Warning disappears, results show adequate fit.

@@

Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).

@@

We see that Communication is severely skewed. Let's calculate how many participants actually commented.

@@

@@

```{r cache=F}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR02_01 + TR02_02 + TR02_03
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  Words_log =~ words_log

@@

We first report the factor validity of all variables combined.

@@

# add centered predictors for interaction analyses later
d %<>%
  mutate(
    pri_con_fs_c = scale(pri_con_fs, scale = FALSE),
    grats_spec_fs_c = scale(grats_spec_fs, scale = FALSE),
    pri_del_fs_c = scale(pri_del_fs, scale = FALSE),
    trust_gen_fs_c = scale(trust_gen_fs, scale = FALSE),
    self_eff_fs_c = scale(self_eff_fs, scale = FALSE),
    male_c = scale(male, scale = FALSE),
    edu_c = scale(edu, scale = FALSE),
    age_c = scale(age, scale = FALSE),
    con_x_del = pri_con_fs_c * pri_del_fs_c,
    grats_x_del = grats_spec_fs_c * pri_del_fs_c
    )

@@

In what follows, we report zero-order correlations, distributions, and scatterplots of the variables' factor scores.

@@

In what follows, we report power analyses for our study. Please note that we conduct a rudimentary power-analysis, assuming bivariate correlations. To explain, at the time we were not yet aware of the existence of power analyses for multivariate structural equation models.

@@

We first estimate the sample size necessary to find small effects in 95% of all cases.

@@

We then compute the power we have achieved with our finale sample size to detect small effects.

@@

We finally compute what effect size we are likely to find in 95% of all cases given our final sample size.

@@

Shows that multivariate normal distribution is violated. We hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.

@@

[Note: These lines stopped working after some time, potentially due to changes in package.]

In what follows we test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.

@@

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider

@@

In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.

@@

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider

@@

We first compare likes and likes plus dislikes to the control condition.

@@

We then compare likes and likes plus dislikes to the control condition.

@@

We then compare likes and likes plus dislikes to the control condition.

@@

save(
  d_raw, d_all, d_fs, d
  , fit_baseline, fit_prereg
  # , fig_fs_m, fig_fs_cor, fig_coeffs
  , des_pridel
  , facval_tab
  , n_comments, n_desired, n_posts, n_speeding, n_time, n_words
  , n_users, n_final
  # , infl_cases, infl_cases_tokens
  , resp_pattern, n_resp_pattern
  , n_t1, age_t1_m, male_t1_m, college_t1_m
  , n_t2, age_t2_m, male_t2_m, college_t2_m
  , n_matched, n_final, age_final_m, male_final_m, college_final_m, words_m
  , r_sesoi, r_sensitive, power_achieved
  , no_words_perc
  , effects_wrds_selfeff_12, effects_wrds_selfeff_67, effect_lkdlk_prcnt
  , wrds_pricon_7, wrds_pricon_1, wrds_selfeff_1, wrds_selfeff_7
  , tab_slopes
  , file = "data/workspace.RData"
)
```

>>>>

Let's first load the packages we require for our analyses. Note that some need to be installed manually from github.

@@

# define packages
packages <- 
  c(
    "brms", 
    "cowplot", 
    "devtools", 
    "english", 
    "faoutlier", 
    "GGally",
    "kableExtra", 
    "knitr", 
    "lavaan", 
    "magrittr",
    "marginaleffects",
    "MVN",
    "pwr", 
    "quanteda", 
    "semTools", 
    "tidyverse", 
    "td"
    )

@@

We now build some custom functions required for the analyses. Note that here you can find the syntax for the main analyses wrapped in helper functions, which we will then call below.

@@

Let's next tidy up and prepare the data, so we can analyze them.

@@

    # take logarithm
    words_log = log1p(words),
    self_dis_log = log1p(self_dis)
  )

@@

I filtered participants who answered the questionnaire in less than three minutes, which I considered to be unreasonably fast.

@@

I inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.

@@

@@

# Measures

Let's next inspect all measures. I list all items, their distributions and CFAs.

## Privacy concerns
### Items

@@

Model fit was good.

@@

Model fit was okay.

@@

Model fit was very good (which is nice, given it's a newly designed scale).

@@

 1. The other users seemed trustworthy.  
 2. The operators of the participation platform seemed trustworthy.  
 3. The website seemed trustworthy.

@@

Note that I constrained two loadings to be able to report model fit. I used operators and website, as these are theoretically closer.

@@

Note that I constrained Items 5 and Item 9 to be equal. Explanation: First, they are theoretically related. Second, not constraining would yield to just-identified model, for which model fit cannot be interpreted meaningfully.

@@

```{r}
name <- "trustspec"
model <- "
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09

  trust_spec =~ trust_community + trust_provider + trust_system
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

@@

Model fit was good (there's a Highwood case on level 1, which is not too problematic in this case.)

@@

Shows significant misfit. I will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).

@@

We can see that Communication is severely skewed. Let's calculate how many participants actually commented.

@@

`r no_words_perc` percent wrote a comment. The average number of communicated words was `r words_m`.

@@

```{r cache=F}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR02_01 + TR02_02 + TR02_03
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09
  trust_spec =~ trust_community + trust_provider + trust_system
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  Words_log =~ words_log

@@

I first report the factor validity of all variables combined.

@@

@@

In what follows, I report zero-order correlations, distributions, and scatterplots of the variables' factor scores.

@@

In what follows, I report power analyses for our study. Please note that I conduct a rudimentary power-analysis, assuming bivariate correlations. (At the time I was not yet aware of the existence of power analyses for multivariate structural equation models.)

@@

I first estimate the sample size necessary to find small effects in 95% of all cases.

@@

I then compute the power we have achieved with our final sample size to detect small effects.

@@

I finally compute what effect size we are likely to find in 95% of all cases given our final sample size.

@@

Shows that multivariate normal distribution is violated. I hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.

@@

In what follows I test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, I compute Cook's distance.

[Note: The following lines stopped working after some time, potentially due to changes in package. I can hence not recreate them here, but refer to results obtained before.]

@@

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09

  trust_spec =~ trust_community + trust_provider + trust_system

@@

In what follows, I also report explicit statistical tests of the differences between the conditions using contrasts.

@@

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09
  trust_spec =~ trust_community + trust_provider + trust_system

@@

I first compare likes and likes plus dislikes to the control condition.

@@

I then compare likes and likes plus dislikes to the control condition.

@@

I then compare the likes and control conditions to the likes plus dislikes condition.

@@

save(
  d_raw, d_all, d_fs, d
  , fit_baseline, fit_prereg
  , des_pridel
  , facval_tab
  , n_comments, n_desired, n_posts, n_speeding, n_time, n_words
  , n_users, n_final
  , resp_pattern, n_resp_pattern
  , n_t1, age_t1_m, male_t1_m, college_t1_m
  , n_t2, age_t2_m, male_t2_m, college_t2_m
  , n_matched, n_final, age_final_m, male_final_m, college_final_m, words_m
  , r_sesoi, r_sensitive, power_achieved
  , no_words_perc
  , effects_wrds_selfeff_12, effects_wrds_selfeff_67, effect_lkdlk_prcnt
  , wrds_pricon_7, wrds_pricon_1, wrds_selfeff_1, wrds_selfeff_7
  , tab_slopes
  , file = "data/workspace.RData"
)
```
